Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-21 Ben_Manuscripts/structure_paper/Draft.tex
Edits after full read-through

  The H\textsubscript{II} phase pore geometry has a higher theoretical capacity
  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014}. 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

%  We used experimental small-angle X-ray scattering (SAXS) data from
%  \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
%  (WAXS) data (Fig.~\ref{fig:WAXS}, produced as described in
%  \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
%  since it encodes all structural details down to the sub-nm scale.  
  There are five major features of interest present in the 2D experimental pattern shown 
  in Figure \ref{fig:WAXS}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to real
	space periodicity of 7.4 \AA. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the $z$ axis\cite{feng_scalable_2014}, meaning that if one traces the 
	positions of the aromatic rings with a helical curve, then for each full turn 
	in the helix, one will encounter two aromatic rings.

	\item \textit{R-alkanes}: A low intensity ring located at r = 1.4
	\AA$^{-1}$ marks the third major reflection of interest. The real space
	separation corresponds to 4.5 \AA~ which is characteristic of the average
	spacing between packed alkane chains \cite{mcintosh_organization_1980}. We will
	call this reflection R-alkanes.

@@

	\item \textit{R-pores}: The final feature corresponds to the spacing
	and symmetry of the d\textsubscript{100} plane. This plane is geometrically
	related the distance between pores. The feature, which we named R-pores, is
	characterized by dots along the equatorial axis defined by $q_z$ = 0. The
	spacing between dots is indicative of the hexagonal symmetry of the packed
	pores. We observe the same information with higher resolution using SAXS
	(Fig.~\ref{fig:SAXS}).

@@

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}[t]{0.405\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) (Reproduced from \citenum{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

	While the Col\textsubscript{h} phase is described as dry, it is likely
	that small amounts of ambient water are absorbed into the system. The hydrogen
	bonding network formed by the water may play a role in structuring the pore. We
	used simulated X-ray diffraction (XRD) patterns to see if there is any
	meaningful structural difference between a "dry" and a "wet" system.

@@

  We measured the one dimensional pair distribution function, $g(z)$, between centers 
  of masses of aromatic head group rings along the z-axis (perpendicular to
  the membrane plane). We averaged all 1D slices in the z-direction of the full 3D 
  correlation function within 2.1~\AA~of $(x, y)=(0, 0)$. We chose 2.1 \AA~as a crude 
  approximation of the radius of the phenyl ring plane. 
  %In this way, we include any instances of 
  %overlapping electron density which would contribute to R-$\pi$. 
  We calculated the radius as the sum of the longest C-C distance within a phenyl 
  ring (2.8~\AA) and two times the carbon atom radius (0.7~\AA).

  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
  average distance between stacked monomers, and an amplitude that decays exponentially
  (see Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
  to a decaying exponential function of the form:
  \begin{equation}
  	Ae^{-z/L}
  	\label{eqn:decaying_exponential}
  \end{equation}
  where A is a fitting parameter for amplitude, z is the independent variable of $g(z)$ 
  and L is the fit correlation length. We calculated the error in the estimated value
  of L as the square root of the diagonal entry of the covariance matrix of 
  optimized fit parameters.  %BJC6: reference scipy curve_fit?

  \subsubsection{\textit{Simulated structure factor calculations}}\label{method:xrd}

  We generated simulated XRD patterns based on atomic coordinates in order to make
  a direct experimental comparison. We modeled all atomic coordinates as Gaussian
  spheres of electron density corresponding to each atom's electronic radius. A 
  three dimensional Fourier transform (FT) of the array of electron density results in a three dimensional
  structure factor which represents the unit cell in reciprocal space. The
  experimental WAXS measurement was made using a vertically aligned film whose 
  pores were oriented perpendicular to the direction of the incident X-ray beam. 
  %BJC6: Below is the part I'm having a hard time putting into words. 
  Although the pores were vertically aligned, the crystalline domains were still
  misaligned with respect to the xy plane. To account for this, we averaged
  2D slices of the structure factor at all angles about $|\mathbf{q}| = (0, 0, z)$.

@@

  We measured the intensity of R-pores based on the intensity of the leading peak
  (closest to $q_r$ = 0) of the $q_r$ cross-section of the patterns at $q_z$=0
  (Figure~\ref{fig:saxs_xsection}). The beamstop covers most of the small angle
  reflections in the experimental 2D WAXS pattern. In order to compare the simulated
  intensity of R-pores to experiment, we used the $q_r$ cross-section of 2D SAXS 
  which was generated from the same sample. Since the d\textsubscript{110} peak is  %BJC12: verify which crystal plane it is.
  partially exposed in the experimental 2D WAXS pattern, we normalized the experimental 
  2D SAXS cross-section by matching the intensity of the d\textsubscript{110} peak 
  between it and the experimental 2D WAXS cross-section. It is possible that the peak
  is not fully captured in the 2D WAXS pattern and that our estimate of the intensity
  of R-pores for the experimental pattern is underestimated.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{ralkanes.png}
  \caption{R-alkanes}\label{fig:ralkanes}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rpi_rdouble.png}
  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{angular_integration.png}
  \caption{R-spots}\label{fig:rspots}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{saxs_xsection.png}
  \caption{R-spots}\label{fig:saxs_xsection}
  \end{subfigure}
  \caption{(a) We measured the intensity of R-alkanes by calculating the average 
  intensity within the region bounded by $|\mathbf{q}|$ = 1.4$\AA^{-1}$ and 
  1.57$\AA^{-1}$ (between 4.0 and 4.5 \AA in real space). We excluded intensities
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
  simulated patterns differ from experiment in those regions in all cases. (b) We
  measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
  cross-section of the diffraction pattern. (c) We measured the intensity of R-spots
  by averaging the peak heights produced by radially integrating the patterns within 
  the R-alkanes region. We took the intensity of R-spots as the average of the 
  peak intensities near 37 and 143 $\degree$. (d) We measured the intensity of 
  R-pores by measuring the height of the leading peak (closest to $q_r$=0) of 
  the cross-section of the diffraction patterns along the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
  \end{figure}

@@

  We calculated ionic conductivity using the Nernst-Einstein relationship, which 
  relates the DC ionic conductivity, $\sigma$, to ion diffusivity, $D$, 
  concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
  temperature, $T$: 
  \begin{equation}
	\sigma = \dfrac{q^2CD}{k_b T} 
	\label{eqn:nernst_einstein}
  \end{equation}
  We measured sodium ion diffusion coefficients by calculating the slope
  of the linear region of the z-direction mean square displacement curve as
  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
  visualized the MSD plot to determine where to begin and end a linear fit. We
  measured ion concentration with respect to the volume of the entire unit cell. 
  More details are provided in the Supporting Information, Section~S-\ref{S-section:ionic_conductivity}.

  In order to gain a deeper understanding of discrepancies between the experimental and
  and simulated R-$\pi$ reflection, we used a simplified baseline model where we 
  represent each monomer as a single point scatterer located at the center of mass
  of its head group. In order to make a system approximately similar to our equilibrated 
  simulation geometries, we created 4 hexagonally packed pore regions spaced 42.5 \AA 
  apart, each with 5 columns of scatterers spaced 4.4 \AA apart in the $z$-direction. We
  built the system 4 times taller in the $z$-direction (80 scatterers per column) in order
  to access higher $q_z$ resolution.

  We approximated interactions between particles by correlating the $z$-distance 
  between points within each column of point scatterers. We placed points in each
  column by drawing random samples from a multivariate normal distribution defined
  by the mean positions of an equally spaced column of points. We gave the 
  distribution at each point along the column the same standard deviation, 
  $\sigma_z$ and we defined a covariance matrix such that the covariance, $v$, of
  the distance, $d$, between scatterers decays exponentially from $v$ according
  to the equation $ve^{-d/L}$, where $L$ is the correlation length. We used the
  experimental correlation length of 9.0 $\AA$.

@@

  Our simulations best support a model built with 5 monomer columns per pore based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question \ref{point:monomernum} above, we ran
  simulations of systems created with 4--8 columns per pore. We built systems in both
  the parallel displaced and sandwiched configurations and equilibrated them according
  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional 
  systems with monomers initially spaced 5 \AA~apart vertically (see section~\ref{S-section:initial_pore_spacing}
  of the Supporting Information for more details on sensitivity to initial layer spacing). 
  We considered the pore-to-pore spacing to be equilibrated as defined in section~\ref{method:equil_time}.
  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested.

@@

  We can better understand the structure of the system by simulating X-ray
  diffraction patterns produced from equilibrated MD trajectories and comparing
  them to experiment (see section~\ref{method:xrd}). We tested systems built with
  5 columns per pore in the parallel displaced and sandwiched configurations at
  300 K in the ordered and disordered basins, as those were the most consistent
  with the most unambiguous X-ray diffraction features, the pore-to-pore spacing
  and the stacking distance.  We generated simulated patterns using the locally
  equilibrated portion of each simulation trajectory (See
  Section~\ref{method:equil_time}. There are two important factors to take into
  account when looking at differences between experimental XRD and simulated XRD.
  First, the simulated diffraction patterns have some noise, especially along the
  $q_z$ axis at $q_r$=0, which is where several of the more interesting features
  are located. This is due to the angle averaging of the 3D structure factor
  around the $q_z$-axis, meaning there are fewer samples as  $q_r$ approaches 0.
  The amount of samples required to to converge along the $q_z$ axis is analyzed
  in Supporting Information section S-\ref{S-section:xrd_noise}.  More
  importantly, our simulations do not appear to be long enough to sample truly
  independent configurations within their respective metastable basins (see
  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting
  the results of the XRD. The simulated patterns generated for all systems
  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.

@@

  The simulated XRD patterns show moderate agreement with experiment. There 
  are key qualitative and quantitative differences between the experimental and simulated
  locations and intensities of each major reflection. The integrated intensity and location
  of each simulated reflection relative to its experimental counterpart are shown in  
  Table~\ref{table:relative_intensities_300K}. Our approach for measuring the intensity of
  each reflection are described in section S-\ref{S-section:xrd_intensities}. 
  %MRS12: should that be in Methods instead of suporting?  Not sure.
  %BJC12: moved into methods for now.

  In the next few subsections, we individually address each major reflection, and the
  similarities and differences between simulation and experiment. We start with relatively 
  uncomplicated analyses of reflections that are very similar between experiment and simulation:
  \begin{itemize}
  	\item The location of R-alkanes (section~\ref{section:ralkanes})
  	\item The intensity of R-pores (section~\ref{section:rpores})
  \end{itemize}
  and then move onto more complicated explanations of those reflections whose characteristics
  do not match, or have not been fully explained by experiment:
  \begin{itemize}
  	\item The origin of R-spots (section~\ref{section:rspots})
  	\item The position, shape and intensity of R-$\pi$ (section~\ref{section:rpi})
  	\item The origin of R-double (section~\ref{section:rdouble})
  \end{itemize}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 12.3       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  %MRS12: question: is the normalization for the simulated systems the same, no matter if disordered, etc.  If not chosen to be exactly the same, how different are they?
  %BJC12: Are you asking what the normalization constant is that I divide the patterns by for each system? I'll have to check. 
  \caption{The simulated XRD patterns of the systems tested, normalized so that
	  the average intensity of R-alkanes in each pattern equals 1, show R-pores and
	  R-$\pi$ reflections that are significantly higher than experiment and R-spots
	  reflections that are slightly lower than experiment. R-double does not appear
	  in any simulated patterns, and thus has no measurable intensity.}
  \label{table:relative_intensities_300K} 
  \end{table}

@@

  With the structural understanding gained by these simulations, it becomes
  possible evaluate transport of various solutes within the system, and apply the
  knowledge gained from this study in order to suggest improvements to the
  existing system as well as to evaluate new unsynthesized LLC systems.

>>>>

  The H\textsubscript{II} phase pore geometry (Figure~\ref{fig:assembly}) has a
  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
  The H\textsubscript{II} phase forms at room temperature in the presence of
  c.a.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
  form the same hexagonal columnar structure which, in literature, has been
  referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014}. 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

%  We used experimental small-angle X-ray scattering (SAXS) data from
%  \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
%  (WAXS) data (Fig.~\ref{fig:WAXS}, produced as described in
%  \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
%  since it encodes all structural details down to the sub-nm scale.  
  There are five major features of interest present in the 2D experimental
  pattern shown in Figure~\ref{fig:WAXS}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to real
	space periodicity of 7.4 \AA. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, we will refer to it as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the $z$ axis\cite{feng_scalable_2014}.
        %meaning if one traces the 
	%positions of the aromatic rings with a helical curve, then for each full turn 
	%in the helix, one will encounter two aromatic rings.

	\item \textit{R-alkanes}: A low intensity ring located at $|\mathbf{q}|$ = 1.4
	\AA$^{-1}$ marks the third major reflection of interest. The real space
	separation corresponds to 4.5 \AA~ which is characteristic of the average
	spacing between packed alkane chains \cite{mcintosh_organization_1980}. We will
	call this reflection R-alkanes.

@@

	\item \textit{R-pores}: The final feature corresponds to the spacing
	and symmetry of the pore columns. 
        %d\textsubscript{100} plane. This plane is geometrically
        %related the distance between pores.
	The feature, which we named R-pores, is characterized by reflections along the
	equatorial axis defined by $q_z$ = 0. The spacing between dots is indicative of
	the hexagonal symmetry of the packed pores. We observe the same information
	with higher resolution using SAXS (Fig.~\ref{fig:SAXS}).

@@

  \begin{figure}[!htb]
        \centering
                \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\begin{subfigure}[t]{0.405\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
	\caption{(a) 2D WAXS gives details about repeating features on the
		order of angstroms. Experimentalists have explained each of the 5 major
		reflections present as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack
		3.7 \AA~apart. (R-double) Monomers arrange vertically in a 2\textsubscript{1}
		helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer
		tails are tilted with respect to the membrane plane. (R-pores) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
		from \citenum{feng_thin_2016}) The repeat spacing in the 1D small angle X-ray
		scattering pattern is characteristic of hexagonal packing. The leading peak,
		q*, represents the distance between the d\textsubscript{100} planes. Using this
		distance, we know that the distance between pore centers is 4.12 nm.} 
	\label{fig:SWAXS}
 \end{figure}

@@

	While the Col\textsubscript{h} phase is described as dry, it is likely
	that small amounts of ambient water are absorbed into the system. The hydrogen
	bonding network formed by the water may play a role in structuring the pore. We
	used simulated X-ray diffraction (XRD) patterns to uncover any 
        %see if there is any
	meaningful structural difference between a "dry" and a "wet" system.

@@

  \subsubsection{\textit{Generation of simulated X-ray diffraction patterns}}\label{method:xrd}

  We generated simulated XRD patterns based on atomic coordinates in order to
  make a direct experimental comparison. We modeled all atomic coordinates as
  Gaussian spheres of electron density whose maximum and width are defined by
  each atom's atomic number electronic radius respectively. A three dimensional
  Fourier transform (FT) of the array of electron density results in a three
  dimensional structure factor which represents the unit cell in reciprocal
  space. The experimental WAXS measurement was made using a vertically aligned
  film whose pores were oriented perpendicular to the direction of the incident
  X-ray beam. 
  %BJC6: Below is the part I'm having a hard time putting into words. 
  Although the pores are vertically aligned, the crystalline domains are
  still misaligned with respect to the $xy$ plane. To account for this, we averaged
  2D slices of the structure factor at all angles about $|\mathbf{q}| = (0, 0, z)$.

@@

  We measured the intensity of R-pores based on the intensity of the
  d\textsubscript{100} peak (the leading peak closest to $q_r$ = 0) of the $q_r$
  cross-section of the patterns at $q_z$=0 (Figure~\ref{fig:saxs_xsection}). The
  beamstop covers most of the small angle reflections in the experimental 2D WAXS
  pattern. In order to compare the simulated intensity of R-pores to experiment,
  we used the $q_r$ cross-section of 2D SAXS which was generated from the same
  sample (Figure S-TBD). Since the d\textsubscript{110} peak is
  %BJC12: verify which crystal plane it is.  
  partially exposed in the experimental 2D WAXS pattern, we normalized the
  experimental 2D SAXS cross-section by matching the intensity of the
  d\textsubscript{110} peak between it and the experimental 2D WAXS
  cross-section. It is possible that the peak is not fully captured in the 2D
  WAXS pattern and that we have underestimated the intensity of R-pores in the
  experimental pattern.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{ralkanes.png}
  \caption{R-alkanes}\label{fig:ralkanes}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rpi_rdouble.png}
  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{angular_integration.png}
  \caption{R-spots}\label{fig:rspots}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{saxs_xsection.png}
  \caption{R-spots}\label{fig:saxs_xsection}
  \end{subfigure}
  \caption{(a) We measured the intensity of R-alkanes by calculating the average 
  intensity within the region bounded by $|\mathbf{q}|$ = 1.4~$\AA^{-1}$ and 
  1.57~$\AA^{-1}$ (between 4.0 and 4.5 \AA~in real space). We excluded intensities
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
  simulated patterns differ from experiment in those regions in all cases. (b) We
  measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
  cross-section of the diffraction pattern. (c) We measured the intensity of R-spots
  by averaging the peak heights produced by radially integrating the patterns within 
  the R-alkanes region. We took the intensity of R-spots as the average of the 
  peak intensities near 37 and 143$\degree$. (d) We measured the intensity of 
  R-pores by measuring the height of the d\textsubscript{100} peak (the leading
  peak closest to $q_r$=0) of the cross-section of the diffraction patterns along
  the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
  \end{figure}

  We measured the one dimensional pair distribution function, $g(z)$, between centers 
  of masses of aromatic head group rings along the z-axis (perpendicular to
  the membrane plane). We averaged all 1D $z$-directional slices of the full 3D 
  correlation function within 2.1~\AA~of $(x, y)=(0, 0)$. We chose 2.1 \AA~as a crude 
  approximation of the radius of the phenyl ring plane. 
  %In this way, we include any instances of 
  %overlapping electron density which would contribute to R-$\pi$. 
  We calculated the radius as the sum of the longest C-C distance within a phenyl 
  ring (2.8~\AA) and two times the carbon atom radius (0.7~\AA). % citation

  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
  average distance between stacked monomers, and an amplitude that decays exponentially
  (see Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
  to a decaying exponential function of the form:
  \begin{equation}
  	Ae^{-z/L}
  	\label{eqn:decaying_exponential}
  \end{equation}
  where A is a fitting parameter for amplitude, $z$ is the independent variable of $g(z)$ 
  and L is the fit correlation length. We calculated the error in the estimated value
  of L as the square root of the diagonal entry of the covariance matrix of 
  optimized fit parameters.  %BJC6: reference scipy curve_fit?

  In order to gain a deeper understanding of discrepancies between the experimental and
  and simulated R-$\pi$ reflection, we used a simplified baseline model where we 
  represent each monomer as a single point scatterer located at the center of mass
  of its head group. In order to make a system approximately similar to our equilibrated 
  simulation geometries, we created 4 hexagonally packed pore regions spaced 42.5 \AA~ 
  apart, each with 5 columns of scatterers spaced 4.4 \AA~apart in the $z$-direction. We
  built the system 4 times taller in the $z$-direction (80 scatterers per column) in order
  to access higher $q_z$ resolution.

  We approximated interactions between particles by correlating the $z$-distance 
  between points within each column of point scatterers. We placed points in each
  column by drawing random samples from a multivariate normal distribution defined
  by the mean positions of an equally spaced column of points. We gave the 
  distribution at each point along the column the same standard deviation, 
  $\sigma_z$ and we defined a covariance matrix such that the covariance, $v$, of
  the distance, $d$, between scatterers decays exponentially from $v$ according
  to the equation $ve^{-d/L}$, where $L$ is the correlation length. Unless noted
  otherwise, we used the experimental correlation length of 9.0 $\AA$.

@@

  We calculated ionic conductivity using the Nernst-Einstein relationship, which 
  relates the DC ionic conductivity, $\sigma$, to ion diffusivity, $D$, 
  concentration, $C$, ion charge, $q$, the Boltzmann constant, $k_b$, and 
  temperature, $T$: 
  \begin{equation}
	\sigma = \dfrac{q^2CD}{k_b T} 
	\label{eqn:nernst_einstein}
  \end{equation}
  We measured sodium ion diffusion coefficients by calculating the slope
  of the linear region of the $z$-direction mean square displacement curve as
  indicated by the Einstein relation \cite{einstein_investigations_1956}. We
  visualized the MSD plot to determine where to begin and end a linear fit. We
  measured ion concentration with respect to the volume of the entire unit cell. 
  More details are provided in the Supporting Information, Section~S-\ref{S-section:ionic_conductivity}.

@@

  Our simulations best support a model built with 5 monomer columns per pore based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing Question \ref{point:monomernum} above, we ran
  simulations of systems created with 4--8 columns per pore. We built systems in both
  the parallel displaced and sandwiched configurations and equilibrated them according
  to the dry equilibration procedure. We tested all systems with an initial vertical monomer 
  spacing, $\mathit{d}$, of 3.7 \AA~in accordance with R-$\pi$. We tested 4 additional 
  systems with monomers initially spaced 5 \AA~apart vertically (see section~\ref{S-section:initial_pore_spacing}
  of the Supporting Information for more details on sensitivity to initial layer spacing). 
  We considered the pore-to-pore spacing to be equilibrated as defined in section~\ref{method:equil_time}.
  Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems tested.

@@

  We can better understand the structure of the system by simulating X-ray
  diffraction patterns produced from equilibrated MD trajectories (see
  section~\ref{method:xrd}) and comparing them to experiment, addressing
  Question~\ref{point:xrdmatch}. We tested systems built with 5 columns per pore
  in the parallel displaced and sandwiched configurations at
  300 K in the ordered and disordered basins, as those were the most consistent
  with the most unambiguous X-ray diffraction features, the pore-to-pore spacing
  and the stacking distance.  We generated simulated patterns using the locally
  equilibrated portion of each simulation trajectory (See
  Section~\ref{method:equil_time}). There are two important factors to take into
  account when looking at differences between experimental XRD and simulated XRD.
  First, the simulated diffraction patterns have some noise, especially along the
  $q_z$ axis at $q_r$=0, which is where several of the more interesting features
  are located. This is due to the angle averaging of the 3D structure factor
  around the $q_z$-axis, meaning there are fewer samples as  $q_r$ approaches 0.
  The amount of samples required to to converge along the $q_z$ axis is analyzed
  in Supporting Information section S-\ref{S-section:xrd_noise}.  More
  importantly, our simulations do not appear to be long enough to sample truly
  independent configurations within their respective metastable basins (see
  section~\ref{section:slow_dynamics}), meaning we must take care in interpreting
  the results of the XRD. The simulated patterns generated for all systems
  studied are shown and compared to experiment in Figure~\ref{fig:XRDsim}.

@@

  The simulated XRD patterns show moderate agreement with experiment. There 
  are key qualitative and quantitative differences between the experimental and simulated
  locations and intensities of each major reflection. The integrated intensity and location
  of each simulated reflection relative to its experimental counterpart are shown in  
  Table~\ref{table:relative_intensities_300K}. Our approach for measuring the intensity of
  each reflection is described in Section~\ref{method:xrd}. 
  %MRS12: should that be in Methods instead of suporting?  Not sure.
  %BJC12: moved into methods for now.

  In the next few subsections, we individually address each major reflection, and the
  similarities and differences between simulation and experiment. We start with relatively 
  uncomplicated analyses of reflections that are very similar between experiment and simulation:
  \begin{itemize}
  	\item The location of R-alkanes (section~\ref{section:ralkanes})
  	\item The location and intensity of R-pores (section~\ref{section:rpores})
  \end{itemize}
  and then move onto more complicated explanations of those reflections whose characteristics
  do not match, or have not been fully explained by experiment:
  \begin{itemize}
  	\item The origin of R-spots (section~\ref{section:rspots})
  	\item The position, shape and intensity of R-$\pi$ (section~\ref{section:rpi})
  	\item The origin of R-double (section~\ref{section:rdouble})
  \end{itemize}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 4.91       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  %MRS12: question: is the normalization for the simulated systems the same, no matter if disordered, etc.  If not chosen to be exactly the same, how different are they?
  %BJC12: Are you asking what the normalization constant is that I divide the patterns by for each system? I'll have to check. 
  \caption{The simulated XRD patterns of the systems tested, normalized so that
	  the average intensity of R-alkanes in each pattern equals 1, show R-pores and
	  R-$\pi$ reflections that are significantly higher than experiment and R-spots
	  reflections that are slightly lower than experiment. R-double does not appear
	  in any simulated patterns, and thus has no measurable intensity.}
  \label{table:relative_intensities_300K} 
  \end{table}

@@

  With the structural understanding gained by these simulations, it becomes
  possible to evaluate transport of various solutes within the system, and apply the
  knowledge gained from this study in order to suggest improvements to the
  existing system as well as to evaluate new unsynthesized LLC systems.
